### 2017-03-10 thesis/discussion/discussion.tex
Finished discussion, now edit everything - tmp commit

% There were two main aims to this project: firstly to determine whether there were any obesity specific genetic signatures that could be tranferred across multiple cancer types; and secondly to investigate whether there were any biological pathways dysregulated in the samples that were obese compared to the samples that were not obese.
% These aims were addressed in \cref{cha:obesity_genetic_signatures_and_cancer,cha:obesity_associated_genetic_signature_and_pathway_signatures}, resepectively, and will be answered in \cref{sec:conclusion}.

@@

% TODO: search for any evidence of BLCA with breast cancers - add to this paragraph
With that said, there is a possibility that the genotypes of the samples that are overweight in \gls{blca} data set are similar to those samples that are obese in the Creighton \textit{et al.} data set.
\textit{(TODO: search for any evidence of relationship/connection between BLCA and breast cancers - add to this paragraph)}

@@

Though how unreliable the Akt pathway metagene scores may be, there is still a possibility that the FM obesity associated genetic signature may be unrelated to the Akt pathway, as Fuentes-Mattei \textit{et al.} validated their human breast tumour-derived genetic signature in a mouse model \citep{Fuentes-Mattei2014}.
Mouse models are indeed helpful in studying biological processes \textit{in vivo}, especially when the cause and the outcome of the disease is well established.
However, cancer is a complex genetic disorder which may be difficult to model accurately in mice.
Furthermore, obesity is a disease that have a variety of biological effects (for example the release of adipokines and the disruption of the hormone levels) that could be acting in a different way in mice compared to humans, which further complicates the causal relationship between obesity and cancer.
Nevertheless, the evidence shown by \citet{Fuentes-Mattei2014} was convincing and the role of Akt/\gls{mtor} pathway in obesity and cancer should be explored in greater details.
\textit{(include this paragraph or not... tbh, I think this is a weak argument)}

@@

This project have managed to show that there were no obesity specific genes  that were common across multiple cancer types.
Although this study failed to identify obesity specific genes that affected tumour biology, it is likely that there is some complex mechanism underlying the relationship between obesity and cancer; otherwise many of the clinical and epidemiological associations between obesity and cancer would not make any sense.
Since Akt, \gls{egfr} and \gls{pr} pathways were signicant in the linear models that predicted the obesity metagenes, more thorough investigation of these pathways may be a good start to clarify the relationship.
The apparent significance of the obesity associated genetic signatures in \gls{blca} data set was interesting as well, and deeper analysis of this data set may help further understand the biology of \gls{blca} and its association with obesity.

>>>>

@@

With that said, there is a possibility that the genotypes of the samples that are overweight in \gls{blca} data set are similar to those samples that are obese in the Creighton \textit{et al.} data set.
In fact, \citet{Damrauer2014} have identified ``basal-like'' and ``luminal''  subtypes in bladder cancer that resembled the corresponding subtypes in breast cancer, and suggested that bladder  and breast cancers may have common physiological properties.
Since all of the obesity associated genetic signatures were derived from breast cancer data sets, it made sense that these signatures were significant in the \gls{blca} data set, as bladder cancer and breast cancer could have been biologically similar to one another.
However, the degree of similarity between these two cancer types are not yet known and further analyses are required for a definitive explanation of the results.

@@

(Though how unreliable the Akt pathway metagene scores may be, there is still a possibility that the FM obesity associated genetic signature may be unrelated to the Akt pathway, as Fuentes-Mattei \textit{et al.} validated their human breast tumour-derived genetic signature in a mouse model \citep{Fuentes-Mattei2014}.
	Mouse models are indeed helpful in studying biological processes \textit{in vivo}, especially when the cause and the outcome of the disease is well established.
	However, cancer is a complex genetic disorder which may be difficult to model accurately in mice.
	Furthermore, obesity is a disease that have a variety of biological effects (for example the release of adipokines and the disruption of the hormone levels) that could be acting in a different way in mice compared to humans, which further complicates the causal relationship between obesity and cancer.
	Nevertheless, the evidence shown by \citet{Fuentes-Mattei2014} was convincing and the role of Akt/\gls{mtor} pathway in obesity and cancer should be explored in greater details.)
\textit{(include this paragraph or not... tbh, I think this is a weak argument)}

@@

This project have managed to show that there were no obesity specific genes  that were common across multiple cancer types.
Although this study failed to identify obesity specific genes that affected tumour biology, it is likely that there is some complex mechanism underlying the relationship between obesity and cancer; otherwise many of the clinical and epidemiological associations between obesity and cancer would not make any sense.
Since Akt, \gls{egfr} and \gls{pr} pathways were signicant in the linear models that predicted the obesity metagenes, more thorough investigation of these pathways may be a good start to clarify the relationship.
Further analyses of \gls{blca} may help clarify the similarity between bladder and breast cancer types and provide an insight into the association between the obesity associated genetic signatures and \gls{blca}.
